---
title: "Processing TCGA variants to annotate structure & AA consequence information"
author: "Joseph Ng"
date: "19 March 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

This markdown contains details to process Mutation Annotation Files (MAFs) downloaded from GDAC Firehose to annotate variants with structure and AA consequences.

The R routine used are printed below; some steps utilised custom python scripts. They are also provided together with bash scripts to indicate the ways to run these scripts on the command line.

# Steps

1. `extractMAF.py` extract relevant columns from the downloaded MAFs.

2. This following routine in R which reads annotation from ZoomVar and label mutations into surface/core/interacting interface.

```{r}
#!/usr/bin/R
cancerTypes = c("ACC", "BLCA", "BRCA", "CESC", "CHOL", "COADREAD", "DLBC", 
                "ESCA", "GBMLGG", "HNSC", "KIPAN", "LAML", "LIHC", "LUAD",
                "LUSC", "OV", "PAAD", "PCPG", "PRAD", "SARC", "SKCM", "STAD", 
                "TGCT", "THCA", "THYM", "UCEC", "UCS", "UVM")
mappingTb = read.table("protein_position_annotations_zoomvar_category_NEW.tsv",
                       header = T, sep = "\t", quote = "", stringsAsFactors = F)

sapply(cancerTypes, function(cancertype){
  print(cancertype)
  input = paste("../TCGA.firehose_maf/",
                cancertype, "_maf_part.txt", sep = "")
  input = read.table(input, header = T, sep = "\t", quote = "", stringsAsFactors = F, fill = T)
  input = input[!is.na(input[, "APOBEC_mutation"]), ]
  input = input[input[, "Variant_Classification"] == "Missense_Mutation", ]

  #Annotate information from Zoomvar output back to input file
  uniprot_col = which(colnames(input) == "SwissProt_acc_Id")
  pos_col = which(colnames(input) == "UniProt_AApos")
  AA_col = which(colnames(input) == "Protein_Change")
  outloc = paste("../TCGA.firehose_maf/", cancertype,
                    "_maf_missense_mapped.txt", sep = "")
  write(paste(c(colnames(input), "struct_cat", "disorder_cat", "origAA", "mutAA"), collapse="\t"), outloc)
  input_anno = t(apply(input, MARGIN = 1, function(x){
    last = nchar(x[AA_col])
    origAA = substr(x[AA_col], 3, 3)
    mutAA = substr(x[AA_col], last, last)
    id = paste(x[uniprot_col], gsub(" ", "", x[pos_col]), sep = "_")
    if (id %in% mappingTb[, 1]){
      entry = mappingTb[mappingTb[, 1] == id, ]
      struct_cat = entry[, "struct_cat"]
      disorder_cat = entry[, "disorder_cat"]
    } else {
      struct_cat = 'None'
      disorder_cat = 'None'
    }
    write(paste(c(x, struct_cat, disorder_cat, origAA, mutAA), collapse = "\t"), outloc, append = T)
    return(c(x, struct_cat, disorder_cat, origAA, mutAA))
  }))
})

```

3. python script `classify_signatures.py` to classify mutations into the signatures of interest (Aging, APOBEC, UV, POLE, 5-FU, Platinum) based on the sequence context surrounding each mutation. This script also contain functionalities to merge two adjacent SNVs to consider double-base substitution (DBS) signatures.

4. R routine to clean up files and annotate AA types. Determine whether mutations involve change in AA type.

```{r}
#!/usr/bin/R
tcga <- list.files("~/TCGA.firehose_maf", 
                   pattern = "maf_allmuttype_mapped_withSig_new.txt",
                   full.names = TRUE)
tcga <- tcga[which(!(grepl("^TCGA", basename(tcga))))]
tcga <- lapply(tcga, function(file){
  tb <- read.table(file, stringsAsFactor = FALSE, sep = "\t", quote = "",
                   comment.char = "", header = TRUE)
  tb$cancerType <- unlist(strsplit(basename(file), split = "_"))[1]
  tb
})
tcga <- do.call("rbind", tcga)
tcga$sample <- substr(tcga$Tumor_Sample_Barcode, 1, 12)

#___________________________
# clean up origAA and mutAA
cleanUpAA <- function(protein_change)
{
  sapply(protein_change, function(p){
    prots <- unlist(strsplit(p, split = ";"))
    nonsyn <- sapply(prots, function(prot){
      wt <- substr(prot, 3, 3)
      mut <- substr(prot, nchar(prot), nchar(prot))
      return(wt != mut)
    })
    paste(prots[nonsyn], collapse = ";")
  })
}
cleanUpCat <- function(cat, protein_change)
{
  sapply(1:length(protein_change), function(p){
    if(grepl(";", cat[p])){
      prots <- unlist(strsplit(protein_change[p], split = ";"))
      nonsyn <- sapply(prots, function(prot){
        wt <- substr(prot, 3, 3)
        mut <- substr(prot, nchar(prot), nchar(prot))
        return(wt != mut)
      })
      paste(cat[p][nonsyn], collapse = ";")
    } else return(cat[p])
  })
}
parseAA <- function(protein_change, out = "wt")
{
  sapply(protein_change, function(p){
    if(grepl(";", p)){
      prots <- unlist(strsplit(p, split = ";"))
    } else prots <- p
    if(out == "wt"){
      return(paste(substr(prots, 3, 3), collapse = ""))
    } else if(out == "mut"){
      return(paste(substr(prots, nchar(prots), nchar(prots)), collapse = ""))
    }
  })
}
# consider separately single-base and compound-base (ie >1 base mutated but 
# still a missense mutation)
compound <- tcga[grepl(";", tcga$Protein_Change), ]
prot_change <- cleanUpAA(compound$Protein_Change)
origAA <- parseAA(prot_change, out = "wt")
mutAA <- parseAA(prot_change, out = "mut")
struct_cat <- cleanUpCat(compound$struct_cat, compound$Protein_Change)
disorder_cat <- cleanUpCat(compound$disorder_cat, compound$Protein_Change)
single <- tcga[!grepl(";", tcga$Protein_Change), ]
compound[, "Protein_Change"] <- prot_change
compound[, "origAA"] <- origAA
compound[, "mutAA"] <- mutAA
compound[, "struct_cat"] <- struct_cat
compound[, "disorder_cat"] <- disorder_cat
tcga <- rbind(single, compound)
rm(single)
saveRDS(tcga, 'TCGA_allmuts_withSig_FINAL.rds')

#____________________________________
# annotate change_type
mapChangeType <- function(tb, colNameWT, colNameMut)
{
  # map whether a missense mutation involves changing AA type
  aa <- list(aromatic = data.frame(aa = c("Y", "W", "F"),
                                   type = rep("aromatic", 3), 
                                   stringsAsFactors = FALSE),
             negative = data.frame(aa = c("E", "D"),
                                   type = rep("negative", 2), 
                                   stringsAsFactors = FALSE),
             positive = data.frame(aa = c("R", "K", "H"),
                                   type = rep("positive", 3), 
                                   stringsAsFactors = FALSE),
             polar = data.frame(aa = c("S", "T", "C", "P", "Q", "N"),
                                type = rep("polar", 6), stringsAsFactors = FALSE),
             nonpolar = data.frame(aa = c("G", "A", "V", "L", "M", "I"),
                                   type = rep("nonpolar", 6), 
                                   stringsAsFactors = FALSE))
  aa <- do.call("rbind", aa)
  wt_col <- which(colnames(tb) == colNameWT)
  mut_col <- which(colnames(tb) == colNameMut)
  tb[, "wt_type"] <- apply(tb, 1, function(x){
    type_wt <- aa[aa[, "aa"] == x[wt_col], "type"]
    if(length(type_wt) == 0) return(NA) else return(type_wt)
  })
  tb[, "mut_type"] <- apply(tb, 1, function(x){
    type_mut <- aa[aa[, "aa"] == x[mut_col], "type"]
    if(length(type_mut) == 0) return(NA) else return(type_mut)
  })
  tb[, "change_type"] <- apply(tb, 1, function(x){
    type_wt <- aa[aa[, "aa"] == x[wt_col], "type"]
    type_mut <- aa[aa[, "aa"] == x[mut_col], "type"]
    if(length(type_wt) == 0 | length(type_mut) == 0) return(NA)
    if(type_wt == type_mut) return(FALSE) else return(TRUE)
  })
  return(tb)
}

single <- tcga[!grepl(";", tcga$Protein_Change), ]
single <- mapChangeType(single, "origAA", "mutAA")
saveRDS(single, 'TCGA_singleAA_withSig_FINAL.rds')

```

