---
title: "Analysing the predictors"
output:
  html_document:
    df_print: paged
---

Plotting and comparing results from the various predictors constructed using Deep Mutational Scanning (experimental /theoretical) datasets.

```{r setup}
knitr::opts_chunk$set(echo = TRUE, fig.path = "predictor_analysis_plots/",
                      dev = "svg")
library(plyr)
library(ggplot2)
dir <- '/media/josefng/My_Passport/'
```

```{r loadData}
# total count of variants
variant_count <- 'variant_counts.txt'
variant_count <- read.table(variant_count, sep = ",", 
                            header = TRUE, stringsAsFactors = FALSE)

roc <- paste0(dir, c('ZoomvarTCGA_rhapsody/prediction/DMSexp/roc_curves_all.csv',
                     'ZoomvarTCGA_rhapsody/prediction/EVmutation/roc_curves_all.csv'))
roc <- lapply(roc, read.table, sep = ",", header = TRUE, stringsAsFactors = FALSE)
roc <- do.call("rbind", roc)
roc$model_name <- factor(roc$model_name, 
                         levels = c("AA + Cons + MutSig + Q(SASA)", 
                                    "AA + Cons + MutSig", "AA + MutSig + Q(SASA)",
                                    "AA + MutSig", "AA only", "MutSig only"))
```

# Number of variants

In the two datasets used for training vs whole databases (ProThermDB, ThermoMutDB).

```{r, fig.width=4.5, fig.height=6}
variant_count[1:2, 'comment'] <- 'Human'
# for ProThermDB and ThermoMutDB, count human and non-human
db_var_count <- variant_count[ which(grepl("Human only", variant_count$dataset)), ]
db_var_count$comment <- 'Human'
db_var_count$dataset <- c('ThermoMutDB', 'ProThermDB')
db_var_count <- rbind(
  db_var_count,
  data.frame(dataset = c('ThermoMutDB', 'ProThermDB'),
             n_variants = c(abs(diff(variant_count[3:4, 'n_variants'])),
                            abs(diff(variant_count[5:6, 'n_variants']))),
             n_proteins = c(abs(diff(variant_count[3:4, 'n_proteins'])),
                            abs(diff(variant_count[5:6, 'n_proteins']))),
             comment = 'other organisms', stringsAsFactors = FALSE)
)
db_var_count <- rbind(db_var_count, variant_count[1:2, ])

#_____________________________
# bar plot, log10 y-axis with break at circa y = 25,000
# ref https://stackoverflow.com/questions/44694496/y-break-with-scale-change-in-r

#Function to transform data to y positions
trans <- function(x){pmin(x, 25000) + 0.005 * pmax(x - 25000,1)}

#Transform n_variants onto the display scale
db_var_count$n_variants_t <- trans(db_var_count$n_variants)
db_var_count$dataset <- factor(
  db_var_count$dataset,
  levels = c("EVmutation", "DMSexp", "", "ProThermDB", "ThermoMutDB")
)

cowplot::plot_grid(
  ggplot(data=db_var_count, aes(x = dataset, y = n_proteins, fill = comment)) +
    geom_bar(stat = 'identity') + cowplot::theme_cowplot() +
    scale_y_log10(name = 'No. of proteins') + 
    scale_fill_manual(values = c('Human' = 'grey', 'other organisms' = 'grey30'),
                      name = "") +
    cowplot::theme_cowplot() +  scale_x_discrete(drop = FALSE) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)),
  ggplot(data=db_var_count, aes(x = dataset, y = n_variants_t, fill = comment)) +
    geom_bar(stat = 'identity') + scale_x_discrete(drop = FALSE) +
    scale_y_continuous(breaks = trans(c(1000, 10000, 100000, 1000000, 5000000)),
                       labels = scales::number(c(1000, 10000, 100000, 1000000,
                                                 5000000), big.mark = ","),
                       name = "No. of variants") +
    cowplot::theme_cowplot() + xlab("") +
    scale_fill_manual(values = c('Human' = 'grey', 'other organisms' = 'grey30'),
                      name = "") +
    geom_rect(aes(xmin=0, xmax=Inf, ymin=trans(25000), ymax=trans(950000)), 
              fill = 'white') + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = 'none'),
  ncol = 1, axis = "lr", align = "v"
)
```

# Score distributions
```{r, fig.height=2, fig.width=6}
# DMSexp
dmsexp <- paste0(dir, 'ZoomvarTCGA_rhapsody/prediction/DMSexp/data/MAVEdb/human_proteins_retained_ready.tsv')
dmsexp <- read.table( dmsexp, header = TRUE, sep= "\t", stringsAsFactors = FALSE )
dmsexp$label <- factor(dmsexp$label, levels = c('0', '1'))

# EVmutation
evmutation <- paste0(dir, 'ZoomvarTCGA_rhapsody/prediction/EVmutation/human_protein_predictions/EVmutation_human_protein_predictions_collapsed_annotated.txt')
evmutation <- read.table( evmutation, header = TRUE, sep= "\t", stringsAsFactors = FALSE )
evmutation$label <- (evmutation$prediction_epistatic < -5)

cowplot::plot_grid(
  ggplot(dmsexp, aes(score, fill = label)) + geom_histogram() +
    cowplot::theme_cowplot() + xlab("DMSexp") +
    scale_fill_manual(values = c('0' = 'grey50', '1' = 'red')) +
    theme(legend.position = 'none'),
  ggplot(evmutation, aes(prediction_epistatic, fill = label)) + geom_histogram() +
    cowplot::theme_cowplot() + 
    scale_fill_manual(values = c('FALSE' = 'grey50', 'TRUE' = 'red')) +
    theme(legend.position = 'none') + 
    scale_x_continuous(breaks = seq(-10, 10, by = 5), name = "EVmutation"),
  nrow = 1, align = "h", axis = "tb"
)
```

# ROC curves

```{r, fig.width=6, fig.height=4}
# performance on respective holdout data
ggplot(roc[which(roc$test_set == 'same proteins' & 
                   roc$model_type == 'all variants' &
                   roc$dataset_name %in% c('EVmutation', 'DMSexp')), ], 
       aes(x = fpr, y = tpr, colour = model_name, group = model_name)) + 
  geom_line(size = 1.3) + cowplot::theme_cowplot() + 
  facet_wrap(~ dataset_name, scales = "free") +
  scale_color_manual(name = "", values = c("#a40000", "#16317d", "#007e2f", "#ffcd12", "#b86092", "#00b7a7")) +
  ylab("True positive rate") + xlab("False positive rate") +
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed', colour = 'grey20') +
  theme(legend.position = 'bottom', legend.text = element_text(size = 9))

```

```{r}
predictor_stats <- read.table('predictor_performance.txt', sep = ",",
                              header = TRUE, stringsAsFactors = FALSE)
predictor_stats$model_name <- factor(predictor_stats$model_name,
                                     unique(predictor_stats$model_name))

# test set: holdout variants
cowplot::plot_grid(
  ggplot(predictor_stats[predictor_stats$test_set == 'same proteins' &
                           predictor_stats$dataset_name %in% c("DMSexp", "EVmutation"), ], aes(x = model_name, y = accuracy, fill = model_type)) +
    geom_bar(stat = "identity", position = position_dodge2(width = 0.5), colour = "black") +
    cowplot::theme_cowplot() + ylab("Accuracy") + xlab("") + 
    facet_wrap(~ dataset_name, ncol = 1) + #ylim(0, 1) +
    scale_fill_manual(values = c("all variants" = "black", "no core" = "white")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "none"),
  ggplot(predictor_stats[predictor_stats$test_set == 'same proteins' &
                           predictor_stats$dataset_name %in% c("DMSexp", "EVmutation"), ], aes(x = model_name, y = f1, fill = model_type)) +
    geom_bar(stat = "identity", position = position_dodge2(width = 0.5), colour = "black") +
    cowplot::theme_cowplot() + ylab("F1 score") + xlab("") + 
    facet_wrap(~ dataset_name, ncol = 1) + #ylim(0, 1) +
    scale_fill_manual(values = c("all variants" = "black", "no core" = "white")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "bottom"),
  ggplot(predictor_stats[predictor_stats$test_set == 'same proteins' &
                           predictor_stats$dataset_name %in% c("DMSexp", "EVmutation"), ], aes(x = model_name, y = roc_auc, fill = model_type)) +
    geom_bar(stat = "identity", position = position_dodge2(width = 0.5), colour = "black") +
    cowplot::theme_cowplot() + ylab("ROC-AUC") + xlab("") +
    facet_wrap(~ dataset_name, ncol = 1) + #ylim(0, 1) +
    scale_fill_manual(values = c("all variants" = "black", "no core" = "white")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "none"),
  nrow = 1, align = "h", axis = "tb"
)

```

```{r}
# test set: BRCA dataset
cowplot::plot_grid(
  ggplot(predictor_stats[predictor_stats$test_set == 'BRCA1 DMS' &
                           predictor_stats$dataset_name %in% c("DMSexp", "EVmutation (exclude BRCA1 & PTEN)"), ], aes(x = model_name, y = accuracy, fill = model_type)) +
    geom_bar(stat = "identity", position = position_dodge2(width = 0.5), colour = "black") +
    cowplot::theme_cowplot() + ylab("Accuracy") + xlab("") + 
    facet_wrap(~ dataset_name, ncol = 1) + #ylim(0, 1) +
    scale_fill_manual(values = c("all variants" = "black", "no core" = "white")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "none"),
  ggplot(predictor_stats[predictor_stats$test_set == 'BRCA1 DMS' &
                           predictor_stats$dataset_name %in% c("DMSexp", "EVmutation (exclude BRCA1 & PTEN)"), ], aes(x = model_name, y = f1, fill = model_type)) +
    geom_bar(stat = "identity", position = position_dodge2(width = 0.5), colour = "black") +
    cowplot::theme_cowplot() + ylab("F1 score") + xlab("") + 
    facet_wrap(~ dataset_name, ncol = 1) + #ylim(0, 1) +
    scale_fill_manual(values = c("all variants" = "black", "no core" = "white")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "bottom"),
  ggplot(predictor_stats[predictor_stats$test_set == 'BRCA1 DMS' &
                           predictor_stats$dataset_name %in% c("DMSexp", "EVmutation (exclude BRCA1 & PTEN)"), ], aes(x = model_name, y = roc_auc, fill = model_type)) +
    geom_bar(stat = "identity", position = position_dodge2(width = 0.5), colour = "black") +
    cowplot::theme_cowplot() + ylab("ROC-AUC") + xlab("") +
    facet_wrap(~ dataset_name, ncol = 1) + #ylim(0, 1) +
    scale_fill_manual(values = c("all variants" = "black", "no core" = "white")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "none"),
  nrow = 1, align = "h", axis = "tb"
)

```

```{r}
# test set: PTEN DMS
cowplot::plot_grid(
  ggplot(predictor_stats[predictor_stats$test_set %in% c("PTEN abundance DMS", "PTEN activity DMS")  &
                           predictor_stats$dataset_name == "EVmutation (exclude BRCA1 & PTEN)", ], aes(x = model_name, y = accuracy, fill = model_type)) +
    geom_bar(stat = "identity", position = position_dodge2(width = 0.5), colour = "black") +
    cowplot::theme_cowplot() + ylab("Accuracy") + xlab("") + 
    facet_wrap(~ test_set, ncol = 1) + #ylim(0, 1) +
    scale_fill_manual(values = c("all variants" = "black", "no core" = "white")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "none"),
  ggplot(predictor_stats[predictor_stats$test_set %in% c("PTEN abundance DMS", "PTEN activity DMS") &
                           predictor_stats$dataset_name == "EVmutation (exclude BRCA1 & PTEN)", ], aes(x = model_name, y = f1, fill = model_type)) +
    geom_bar(stat = "identity", position = position_dodge2(width = 0.5), colour = "black") +
    cowplot::theme_cowplot() + ylab("F1 score") + xlab("") + 
    facet_wrap(~ test_set, ncol = 1) + #ylim(0, 1) +
    scale_fill_manual(values = c("all variants" = "black", "no core" = "white")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "bottom"),
  ggplot(predictor_stats[predictor_stats$test_set  %in% c("PTEN abundance DMS", "PTEN activity DMS") &
                           predictor_stats$dataset_name == "EVmutation (exclude BRCA1 & PTEN)", ], aes(x = model_name, y = roc_auc, fill = model_type)) +
    geom_bar(stat = "identity", position = position_dodge2(width = 0.5), colour = "black") +
    cowplot::theme_cowplot() + ylab("ROC-AUC") + xlab("") +
    facet_wrap(~ test_set, ncol = 1) + #ylim(0, 1) +
    scale_fill_manual(values = c("all variants" = "black", "no core" = "white")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "none"),
  nrow = 1, align = "h", axis = "tb"
)

```

# Comparison with Envision

Envision was also trained with DMS data, but with different datasets & features.

```{r message=FALSE, warning=FALSE}
envision <- read.table(paste0(dir, "ZoomvarTCGA_rhapsody/prediction/Envision/Envision_DMSexppredicted.tsv"), sep = "\t", stringsAsFactors = FALSE, header  =TRUE)
envision <- envision[, c("Uniprot", "position", "AA1", "AA2",
                         "AA_Cons_MutSig_QSASA_p", "AA_Cons_MutSig_p",
                         "AA_MutSig_QSASA_p", "AA_MutSig_p", "AA_p", "MutSig_p", "Envision_predictions")]

# actual DMS scores from the experiments
envision_mavedb <- paste0(dir, "ZoomvarTCGA_rhapsody/prediction/Envision/Envision_MAVEdb_test_set_binary.csv")
envision_mavedb <- read.csv(envision_mavedb, stringsAsFactors = FALSE)

# merge
envision <- merge(envision, envision_mavedb, 
                  by.x = c("Uniprot", "position", "AA1", "AA2"),
                  by.y = c("uniprot", "position", "wt", "variable"),
                  all.x = TRUE, all.y = FALSE, sort = FALSE)
envision <- envision[which(!is.na(envision$value)), ]

# separately for each protein, bin variants by the experimental scores
envision$bin <- ggplot2::cut_number(envision$value, n = 5, 
                                    labels = 1:5)
```

```{r, fig.width=7, fig.height=10}
cowplot::plot_grid(
  ggplot(envision, aes(x = bin, y = AA_Cons_MutSig_QSASA_p)) + geom_boxplot() + facet_wrap(~ Uniprot, ncol = 1) +
    cowplot::theme_cowplot() + ylab("DMSexp damaging probability") +
    ggtitle("DMSexp"),
  ggplot(envision, aes(x = bin, y = 1 - Envision_predictions)) + geom_boxplot() + facet_wrap(~ Uniprot, ncol = 1) +
    cowplot::theme_cowplot() + ylab("1 - Envision prediction") + ggtitle("Envision"),
  nrow = 1, align = "h", axis = "tb"
)

```

```{r}
# pearson/spearman correlation
envision$Envision_prob <- 1 - envision$Envision_predictions
envision_cors <- reshape2::melt(envision, 
                                id.vars = c("Uniprot", "position", "AA1", "AA2",
                                            "value"), 
                                measure.vars = c("AA_Cons_MutSig_QSASA_p",
                                                 "Envision_prob"), value.name = "pred")
cor_results <- ddply(
  envision_cors, c("Uniprot", "variable"),
  summarise,
  n = length(position),
  spearman = cor(value, pred, method = "spearman"),
  pearson = cor(value, pred, method = "pearson")
)
cor_results

```

```{r, fig.width=4, fig.height=3}
cor_results <- reshape2::melt(cor_results, 
                              id.vars = c("Uniprot", "variable",
                                          "n"), 
                              variable.name = "model")
cor_results$variable <- factor(cor_results$variable,
                               labels = c("DMSexp", "Envision"))
cor_results$Uniprot <- factor(cor_results$Uniprot,
                              levels = c("P04035", "P12931", "P63279", 
                                         "Q5SW96", "Q9H3S4"),
                              labels = c("HMGCR", "SRC", "UBE2I",
                                         "LDLRAP1", "TPK1"))

ggplot(cor_results, 
       aes(x = variable, y = Uniprot, fill = -value)) +
  geom_tile() + facet_wrap(~ model) + cowplot::theme_cowplot() +
  scale_fill_gradient2(limits = c(0, 0.6), name = "correlation") +
  geom_text(aes(label = round(-value, 2))) + xlab("") + ylab("") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

# Feature importance

Analysis of the SHAP values putting through the holdout variants.

```{r}
shap_values <- list(
  list.files(pattern = "shap-values.csv", full.names = TRUE,
             path = paste0(dir, "ZoomvarTCGA_rhapsody/prediction/DMSexp")),
  list.files(pattern = "shap-values.csv", full.names = TRUE,
             path = paste0(dir, "ZoomvarTCGA_rhapsody/prediction/EVmutation"))
)
shap_values[[1]] <- lapply(shap_values[[1]], read.csv, check.names = FALSE)
shap_values[[2]] <- lapply(shap_values[[2]], read.csv, check.names = FALSE)
names( shap_values[[1]] ) <- basename(list.files(pattern = "shap-values.csv",
                                                 full.names = TRUE,
             path = paste0(dir, "ZoomvarTCGA_rhapsody/prediction/DMSexp")))
names( shap_values[[2]] ) <- basename(list.files(pattern = "shap-values.csv",
                                                 full.names = TRUE,
             path = paste0(dir, "ZoomvarTCGA_rhapsody/prediction/EVmutation")))
names( shap_values ) <- c("DMSexp", "EVmutation")

features <- colnames( shap_values[[1]][[1]] )
```

```{r, fig.width=6, fig.height=3}
# group features and plot mean absolute SHAP
mean_absolute_shap <- function(tb){
  wt_aa_col <- which(grepl("WT", colnames(tb)))
  if( length(wt_aa_col) > 0 ){
    wt_aa <- apply(tb, MARGIN = 1, function(x) sum(abs(x[wt_aa_col])))
  } else wt_aa <- rep(NA, nrow(tb))
  mut_aa_col <- which(grepl("MUT", colnames(tb)))
  if( length(mut_aa_col) > 0 ){
    mut_aa <- apply(tb, MARGIN = 1, function(x) sum(abs(x[mut_aa_col])))
  } else mut_aa <- rep(NA, nrow(tb))
  mutsig_col <- which(grepl("MutSig", colnames(tb)))
  if( length(mutsig_col) > 0 ){
    mutsig <- apply(tb, MARGIN = 1, function(x) sum(abs(x[mutsig_col])))
  } else mutsig <- rep(NA, nrow(tb))
  cons_col <- which(grepl("PhyloP", colnames(tb)))
  if( length(cons_col) > 0 ){
    cons <- apply(tb, MARGIN = 1, function(x) sum(abs(x[cons_col])))
  } else cons <- rep(NA, nrow(tb))
 qsasa_col <- which(grepl("SASA", colnames(tb)))
  if( length(qsasa_col) > 0 ){
    qsasa <- abs(tb[, qsasa_col])
  } else qsasa <- rep(NA, nrow(tb))
 out <- data.frame( wt_aa = wt_aa, mut_aa = mut_aa, mutsig = mutsig,
                    cons = cons, qsasa = qsasa )
 out$model <- 'GBM'
 out <- reshape2::melt(out, id.vars <- 'model',
                       measure.vars = c("wt_aa", "mut_aa", "mutsig", "cons", "qsasa"))
 out <- ddply( out, 'variable', summarise, 
               lowerq = quantile(value, probs = 0.25, na.rm = TRUE),
               median = quantile(value, probs = 0.5, na.rm = TRUE), 
               upperq = quantile(value, probs = 0.75, na.rm = TRUE))
 out[which(!is.na(out$median)), ]
}

# tables of mean absolute shap (MAS)
MAS_tb <- list(
  lapply(shap_values[[1]], mean_absolute_shap),
  lapply(shap_values[[2]], mean_absolute_shap)
)
MAS_tb[[1]] <- do.call("rbind", lapply(names(MAS_tb[[1]]), function(x){
  tb <- MAS_tb[[1]][[x]]
  tb$model <- gsub("GBM-", "", gsub("_test-set_shap-values.csv", "", x))
  tb$dataset <- "DMSexp"
  tb
}))
MAS_tb[[2]] <- do.call("rbind", lapply(names(MAS_tb[[2]]), function(x){
  tb <- MAS_tb[[2]][[x]]
  tb$model <- gsub("GBM-", "", gsub("_test-set_shap-values.csv", "", x))
  tb$dataset <- "EVmutation"
  tb
}))
MAS_tb <- do.call("rbind", MAS_tb)
MAS_tb$model <- factor(MAS_tb$model, levels = unique(MAS_tb$model))

ggplot(MAS_tb, aes(x = median, xmin = lowerq, xmax = upperq, y = variable)) +
  geom_bar(stat = "identity") + geom_errorbar(width = 0) + 
  cowplot::theme_cowplot() + facet_grid(dataset ~ model) +
  theme(strip.placement = "outside", axis.text.x = element_text(size = 8))# +
  #geom_rect(aes(xmin=trans(0.1), xmax=trans(0.12), ymin = 0,ymax = Inf), 
  #          fill = "white") #+
  #scale_x_continuous(limits = c(0, NA), breaks = trans(c(0, 0.1, 0.5, 1)), 
  #                   labels = c(0, 0.1, 0.5, 1), position = "top")
```

```{r, fig.height=8, fig.width=4}
# tables of shap lowerq/median/upperq per feature
shap_tb <- list(
  lapply(shap_values[[1]], function(tb){
    tb$model <- "GBM"
    tb <- reshape2::melt(tb, id.vars = "model")
    ddply(tb, "variable", summarise, 
          lowerq = quantile(abs(value), probs = 0.25, na.rm = TRUE),
          median = quantile(abs(value), probs = 0.5, na.rm = TRUE), 
          upperq = quantile(abs(value), probs = 0.75, na.rm = TRUE))
  }),
  lapply(shap_values[[2]], function(tb){
    tb$model <- "GBM"
    tb <- reshape2::melt(tb, id.vars = "model")
    ddply(tb, "variable", summarise, 
          lowerq = quantile(abs(value), probs = 0.25, na.rm = TRUE),
          median = quantile(abs(value), probs = 0.5, na.rm = TRUE), 
          upperq = quantile(abs(value), probs = 0.75, na.rm = TRUE))
  })
)
shap_tb[[1]] <- do.call("rbind", lapply(names(shap_tb[[1]]), function(x){
  tb <- shap_tb[[1]][[x]]
  tb$model <- gsub("GBM-", "", gsub("_test-set_shap-values.csv", "", x))
  tb$dataset <- "DMSexp"
  tb
}))
shap_tb[[2]] <- do.call("rbind", lapply(names(shap_tb[[2]]), function(x){
  tb <- shap_tb[[2]][[x]]
  tb$model <- gsub("GBM-", "", gsub("_test-set_shap-values.csv", "", x))
  tb$dataset <- "EVmutation"
  tb
}))
shap_tb <- do.call("rbind", shap_tb)
shap_tb$model <- factor(shap_tb$model, levels = unique(shap_tb$model))

# plot MUT/WT abs-SHAP distributions
aa_shap <- shap_tb[which(grepl("WT|MUT", shap_tb$variable) &
                           grepl("AA", shap_tb$model)), ]
aa_shap$aa <- gsub("WT_AA_|MUT_AA_", "", as.character(aa_shap$variable))
aa_shap$aa <- factor(aa_shap$aa, levels = c("Y", "W", "F", "E", "D", "R", "K",
                                            "H", "S", "T", "C", "P", "Q", "N",
                                            "G", "A", "V", "L", "M", "I"))
aa_shap$type <- sapply(aa_shap$variable, function(x){
  if(grepl("WT", x)) return("WT") else return("MUT")
})
aa_shap$type <- factor(aa_shap$type, levels = c("WT", "MUT"))
ggplot(aa_shap[aa_shap$model == 'AA_Cons_MutSig_QSASA', ],
       aes(y = aa, x = median, xmin = lowerq, xmax = upperq)) + 
  xlab("absolute SHAP value") +
  facet_grid(type ~ dataset) + geom_point() + geom_errorbar(width = 0) +
  cowplot::theme_cowplot() + geom_vline(xintercept = 0, linetype= 'dashed')
```

```{r, fig.width=6, fig.height=7}
ggplot(aa_shap, aes(y = aa, x = type, fill = median)) + 
  xlab("") + facet_grid(dataset ~ model) + geom_tile() + 
  scale_fill_gradient2(name = "median\nabsolute\nSHAP value") +
  cowplot::theme_cowplot()
```