---
title: "Selection pressure in protein surface and core"
author: "Joseph Ng"
date: "5 May 2021"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "variants_selection_plots/",
                      dev = "svg")
library(ggplot2)
library(biomaRt)  
library(plyr)  

```

This markdown contains the following analysis:
  
* comparison of selection pressure in surface vs core

# Selection pressure

Uses `dndscv` package. Consider for each cohort, dN/dS specifically in protein surface vs core.

Three types of samples:
  
* iPSCs cultured in vitro (HipSci)
* TCGA ([mainly] primary tumours)
* Metastatic tumours from ICGC

```{r}
library("dndscv")
#__________________________________
# functions to parse input/output
get_dndscv_input <- function(file, filterCol = "struct_cat", 
                             filter = FALSE, filter_value = NULL)
{
  if(is.character(file)){
    maf <- read.table(file, header = T, sep = "\t", stringsAsFactors = F)
  } else if(is.data.frame(file)){
    maf <- file
  }
  if(isTRUE(filter) & (filterCol %in% colnames(maf)))
  {
    maf <- maf[maf[, filterCol] == filter_value, ]
  }
  # format:
  ##   sampleID chr      pos ref mut
  ## 1 Sample_1   1   871244   G   C
  ## 2 Sample_1   1  6648841   C   G
  ## 3 Sample_1   1 17557072   G   A
  ## 4 Sample_1   1 22838492   G   C
  ## 5 Sample_1   1 27097733   G   A
  ## 6 Sample_1   1 27333206   G   A
  maf <- maf[, c("Tumor_Sample_Barcode", "Chromosome", "End_position", 
                 "Tumor_Seq_Allele1", "Tumor_Seq_Allele2", "Variant_Classification")]
  colnames(maf) <- c("sampleID", "chr", "pos", "ref", "mut", "Variant_Classification")
  return(maf)
}

get_dndscv_output <- function(input)
{
  out <- dndscv(input, min_indel = 1  )
  # global dnds estimates
  global <- out$globaldnds
  # per gene neutrality tests
  pergene <- out$sel_cv
  # map ensembl protein ID to the pergene table
  pergene[, "ensembl_protein_id"] <- sapply(as.character(pergene[, "gene_name"]), function(x){
    prot <- unique(out$annotmuts[which(as.character(out$annotmuts$gene) == x), "pid"])
    if(length(prot) == 0) return(NA)
    if(length(prot) == 1) return(prot)
    if(length(prot) > 1) return(paste(prot, collapse = ";"))
  })
  return(list(pergene = pergene, global = global))
  # return(out)
}

get_dndscv_output_global <- function(input)
{
  if(nrow(input) == 0) return(NULL)
  print(input[1, 1])
  if(sum(input[, 6] == 'Missense_Mutation') == 0){
    return(NULL)
  }
  library(dndscv)
  out <- try( dndscv(input, min_indel = 1, outp = 1,
                     max_coding_muts_per_sample = Inf ) )
  # global dnds estimates
  if(class(out) == 'try-error') return(out)
  else {
    global <- out$globaldnds
    global
  }
}

# Parse dNdScv results into data frames
parse_dNdScv_all <- function(dNdSresults)
{
  do.call("rbind", lapply(names(dNdSresults), function(x){
    tb <- dNdSresults[[x]]
    if(!is.null(tb)){
      dNdS <- tb["wall", "mle"]
      CIlow <- tb["wall", "cilow"]
      CIhigh <- tb["wall", "cihigh"]
      data.frame(sample = x, dNdS = dNdS, cilow = CIlow, cihigh = CIhigh,
                 stringsAsFactors = FALSE)
    } else return(NULL)
  }))
}
parse_dNdScv_struct <- function(surf_results, core_results)
{
  sample_names <- union(names(surf_results), names(core_results))
  do.call("rbind", lapply(sample_names, function(x){
    surf <- surf_results[[x]]
    core <- core_results[[x]]
    if(!is.null(surf)){
      dNdS_surf <- surf["wall", "mle"]
      CIlow_surf <- surf["wall", "cilow"]
      CIhigh_surf <- surf["wall", "cihigh"]
    } else {
      dNdS_surf <- NA; CIlow_surf <- NA; CIhigh_surf <- NA
    }
    if(!is.null(core)){
      dNdS_core <- core["wall", "mle"]
      CIlow_core <- core["wall", "cilow"]
      CIhigh_core <- core["wall", "cihigh"]
    } else {
      dNdS_core <- NA; CIlow_core <- NA; CIhigh_core <- NA
    }
    data.frame(sample = x, dNdS_surface = dNdS_surf, 
               cilow_surface = CIlow_surf, cihigh_surface = CIhigh_surf,
               dNdS_core = dNdS_core, cilow_core = CIlow_core,
               cihigh_core = CIhigh_core, stringsAsFactors = FALSE)
  }))
}
```

```{r eval=FALSE}
# dNdS all tumour + specifically restricted to surface/core
#________________________________________
# TCGA all sample
tcga <- list.files(path = "~/TCGA.firehose_maf", 
                   pattern = glob2rx("*_maf_allmuttype_mapped_withSig_new.txt"),
                   full.names = T)
tcga <- tcga[ which(!grepl("TCGA_", tcga)) ]
tcga <- lapply(tcga, function(file){
  maf <- read.table(file, header = T, quote = "", sep = "\t", stringsAsFactors = F)
  # print(summary(as.factor(maf$Variant_Classification)))
  maf$Chromosome <- sapply(maf$Chromosome, function(x){
    out <- gsub("chr", "", x)
    if (!(out %in% c("X", "Y"))) return(as.numeric(out)) else return(out)
  })
  maf$cohort <- unlist(strsplit(basename(file), split ="_"))[1]
  maf
  #split(maf, maf$Tumor_Sample_Barcode, drop = TRUE)
})
tcga <- do.call("rbind", tcga)
tcga <- list(tcga)# tcga <- split(tcga, tcga$Tumor_Sample_Barcode, drop = TRUE)
tcga_all <- lapply(tcga, get_dndscv_input, filter = FALSE)
tcga_surf <- lapply(tcga, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "surface")
tcga_core <- lapply(tcga, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "core")
#library(parallel)
#no_cores <- 2 
#cl <- makeCluster(no_cores) 
#data("refcds_hg19", package = "dndscv")
#clusterExport(cl, c("gr_genes", "RefCDS")) 
tcga_all <- lapply(tcga_all, get_dndscv_output_global)
# stopCluster(cl)
tcga_surf <- lapply(tcga_surf, get_dndscv_output_global)
tcga_core <- lapply(tcga_core, get_dndscv_output_global)

#________________________________________
# hipsci all sample
hipsci <- "hipsci_unique_ProteinAlteringMutations_noHLA_zoomvar.maf"
hipsci <- read.table(hipsci, header = T, sep = "\t", stringsAsFactors = F)
hipsci$cohort <- 'iPSCs'
hipsci <- list(hipsci)# hipsci <- split(hipsci, hipsci$Tumor_Sample_Barcode, drop = TRUE)
hipsci_all <- lapply(hipsci, get_dndscv_input, filter = FALSE)
hipsci_surf <- lapply(hipsci, get_dndscv_input, filter = TRUE, 
                      filterCol = "struct_cat", filter_value = "surface")
hipsci_core <- lapply(hipsci, get_dndscv_input, filter = TRUE, 
                      filterCol = "struct_cat", filter_value = "core")
hipsci_all <- lapply(hipsci_all, get_dndscv_output_global)
hipsci_surf <- lapply(hipsci_surf, get_dndscv_output_global)
hipsci_core <- lapply(hipsci_core, get_dndscv_output_global)

#________________________________________
# ICGC all sample
icgc <- "ICGC_20190603_All_Metastatic_simple_somatic_mutation_exonic_oncotator_noHLA_zoomvar.maf"
icgc <- read.table(icgc, header = T, sep = "\t", stringsAsFactors = F, quote = '')
icgc$cohort <- sapply(icgc$Center, function(x) unlist(strsplit(x, split = "-"))[1])
icgc <- list(icgc)#icgc <- split(icgc, icgc$Tumor_Sample_Barcode, drop = TRUE)
icgc_all <- lapply(icgc, get_dndscv_input, filter = FALSE)
icgc_surf <- lapply(icgc, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "surface")
icgc_core <- lapply(icgc, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "core")
icgc_all <- lapply(icgc_all, get_dndscv_output_global)
icgc_surf <- lapply(icgc_surf, get_dndscv_output_global)
icgc_core <- lapply(icgc_core, get_dndscv_output_global)

#________________________________________
tcga_all <- data.frame(cohort = "TCGA", genes = "all",
                       dNdS_all = tcga_all[[1]]$mle[1], 
                       cilow_all = tcga_all[[1]]$cilow[1], 
                       cihigh_all = tcga_all[[1]]$cihigh[1],
                       dNdS_surface = tcga_surf[[1]]$mle[1], 
                       cilow_surface = tcga_surf[[1]]$cilow[1], 
                       cihigh_surface = tcga_surf[[1]]$cihigh[1],
                       dNdS_core = tcga_core[[1]]$mle[1], 
                       cilow_core = tcga_core[[1]]$cilow[1], 
                       cihigh_core = tcga_core[[1]]$cihigh[1],
                       stringsAsFactors = FALSE)
saveRDS(tcga_all,file='dNdScv_TCGAallSamples_allmuts.rds')
hipsci_all <- data.frame(cohort = "HipSci", genes = "all",
                         dNdS_all = hipsci_all[[1]]$mle[1], 
                         cilow_all = hipsci_all[[1]]$cilow[1], 
                         cihigh_all = hipsci_all[[1]]$cihigh[1],
                         dNdS_surface = hipsci_surf[[1]]$mle[1], 
                         cilow_surface = hipsci_surf[[1]]$cilow[1], 
                         cihigh_surface = hipsci_surf[[1]]$cihigh[1],
                         dNdS_core = hipsci_core[[1]]$mle[1], 
                         cilow_core = hipsci_core[[1]]$cilow[1], 
                         cihigh_core = hipsci_core[[1]]$cihigh[1],
                         stringsAsFactors = FALSE)
saveRDS(hipsci_all,file='dNdScv_HipSciallSamples_allmuts.rds')
icgc_all <- data.frame(cohort = "ICGC Metastatic", genes = "all",
                       dNdS_all = icgc_all[[1]]$mle[1], 
                       cilow_all = icgc_all[[1]]$cilow[1], 
                       cihigh_all = icgc_all[[1]]$cihigh[1],
                       dNdS_surface = icgc_surf[[1]]$mle[1], 
                       cilow_surface = icgc_surf[[1]]$cilow[1], 
                       cihigh_surface = icgc_surf[[1]]$cihigh[1],
                       dNdS_core = icgc_core[[1]]$mle[1], 
                       cilow_core = icgc_core[[1]]$cilow[1], 
                       cihigh_core = icgc_core[[1]]$cihigh[1],
                       stringsAsFactors = FALSE)
saveRDS(icgc_all,file='dNdScv_ICGCallSamples_allmuts.rds')
```

```{r eval=FALSE}
# dNdS calculated on CGC only - surface/core
cgc <- read.table('CGC_COSMICv86_20181030.tsv',
                  header = TRUE, stringsAsFactors = FALSE, sep = "\t")
cgc <- cgc[which(cgc$Tier == 1), 1]

#________________________________________
# TCGA all sample
tcga <- list.files(path = "~/TCGA.firehose_maf", 
                   pattern = glob2rx("*_maf_allmuttype_mapped_withSig_new.txt"),
                   full.names = T)
tcga <- tcga[ which(!grepl("TCGA_", tcga)) ]
tcga <- lapply(tcga, function(file){
  maf <- read.table(file, header = T, quote = "", sep = "\t", stringsAsFactors = F)
  # print(summary(as.factor(maf$Variant_Classification)))
  maf$Chromosome <- sapply(maf$Chromosome, function(x){
    out <- gsub("chr", "", x)
    if (!(out %in% c("X", "Y"))) return(as.numeric(out)) else return(out)
  })
  maf$cohort <- unlist(strsplit(basename(file), split ="_"))[1]
  maf
  #split(maf, maf$Tumor_Sample_Barcode, drop = TRUE)
})
tcga <- do.call("rbind", tcga)
tcga <- tcga[ which(tcga$Hugo_Symbol %in% cgc), ]
tcga <- list(tcga)#tcga <- split(tcga, tcga$Tumor_Sample_Barcode, drop = TRUE)
tcga_all <- lapply(tcga, get_dndscv_input, filter = FALSE)
tcga_surf <- lapply(tcga, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "surface")
tcga_core <- lapply(tcga, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "core")
tcga_all <- lapply(tcga_all, get_dndscv_output_global)
tcga_surf <- lapply(tcga_surf, get_dndscv_output_global)
tcga_core <- lapply(tcga_core, get_dndscv_output_global)

#________________________________________
# hipsci all sample
hipsci <- "hipsci_unique_ProteinAlteringMutations_noHLA_zoomvar.maf"
hipsci <- read.table(hipsci, header = T, sep = "\t", stringsAsFactors = F)
hipsci$cohort <- 'iPSCs'
hipsci <- hipsci[ which(hipsci$Hugo_Symbol %in% cgc), ]
hipsci <- list(hipsci)#hipsci <- split(hipsci, hipsci$Tumor_Sample_Barcode, drop = TRUE)
hipsci_all <- lapply(hipsci, get_dndscv_input, filter = FALSE)
hipsci_surf <- lapply(hipsci, get_dndscv_input, filter = TRUE, 
                      filterCol = "struct_cat", filter_value = "surface")
hipsci_core <- lapply(hipsci, get_dndscv_input, filter = TRUE, 
                      filterCol = "struct_cat", filter_value = "core")
hipsci_all <- lapply(hipsci_all, get_dndscv_output_global)
hipsci_surf <- lapply(hipsci_surf, get_dndscv_output_global)
hipsci_core <- lapply(hipsci_core, get_dndscv_output_global)

#________________________________________
# ICGC all sample
icgc <- "ICGC_20190603_All_Metastatic_simple_somatic_mutation_exonic_oncotator_noHLA_zoomvar.maf"
icgc <- read.table(icgc, header = T, sep = "\t", stringsAsFactors = F, quote = '')
icgc$cohort <- sapply(icgc$Center, function(x) unlist(strsplit(x, split = "-"))[1])
icgc <- icgc[ which(icgc$Hugo_Symbol %in% cgc), ]
icgc <- list(icgc)#icgc <- split(icgc, icgc$Tumor_Sample_Barcode, drop = TRUE)
icgc_all <- lapply(icgc, get_dndscv_input, filter = FALSE)
icgc_surf <- lapply(icgc, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "surface")
icgc_core <- lapply(icgc, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "core")
icgc_all <- lapply(icgc_all, get_dndscv_output_global)
icgc_surf <- lapply(icgc_surf, get_dndscv_output_global)
icgc_core <- lapply(icgc_core, get_dndscv_output_global)

#________________________________________
tcga_all <- data.frame(cohort = "TCGA", genes = "CGC",
                       dNdS_all = tcga_all[[1]]$mle[1], 
                       cilow_all = tcga_all[[1]]$cilow[1], 
                       cihigh_all = tcga_all[[1]]$cihigh[1],
                       dNdS_surface = tcga_surf[[1]]$mle[1], 
                       cilow_surface = tcga_surf[[1]]$cilow[1], 
                       cihigh_surface = tcga_surf[[1]]$cihigh[1],
                       dNdS_core = tcga_core[[1]]$mle[1], 
                       cilow_core = tcga_core[[1]]$cilow[1], 
                       cihigh_core = tcga_core[[1]]$cihigh[1],
                       stringsAsFactors = FALSE)
saveRDS(tcga_all,file='dNdScv_TCGAallSamples_CGC.rds')
hipsci_all <- data.frame(cohort = "HipSci", genes = "CGC",
                         dNdS_all = hipsci_all[[1]]$mle[1], 
                         cilow_all = hipsci_all[[1]]$cilow[1], 
                         cihigh_all = hipsci_all[[1]]$cihigh[1],
                         dNdS_surface = hipsci_surf[[1]]$mle[1], 
                         cilow_surface = hipsci_surf[[1]]$cilow[1], 
                         cihigh_surface = hipsci_surf[[1]]$cihigh[1],
                         dNdS_core = hipsci_core[[1]]$mle[1], 
                         cilow_core = hipsci_core[[1]]$cilow[1], 
                         cihigh_core = hipsci_core[[1]]$cihigh[1],
                         stringsAsFactors = FALSE)
saveRDS(hipsci_all,file='dNdScv_HipSciallSamples_CGC.rds')
icgc_all <- data.frame(cohort = "ICGC Metastatic", genes = "CGC",
                       dNdS_all = icgc_all[[1]]$mle[1], 
                       cilow_all = icgc_all[[1]]$cilow[1], 
                       cihigh_all = icgc_all[[1]]$cihigh[1],
                       dNdS_surface = icgc_surf[[1]]$mle[1], 
                       cilow_surface = icgc_surf[[1]]$cilow[1], 
                       cihigh_surface = icgc_surf[[1]]$cihigh[1],
                       dNdS_core = icgc_surf[[1]]$mle[1], 
                       cilow_core = icgc_surf[[1]]$cilow[1], 
                       cihigh_core = icgc_surf[[1]]$cihigh[1],
                       stringsAsFactors = FALSE)
saveRDS(icgc_all,file='dNdScv_ICGCallSamples_CGC.rds')
```

```{r eval=FALSE}
# dNdS calculated on essential genes only - surface/core
# VES from zoomvar for the Hart essential gene list
files <- list.files('../ZoomvarBrowserApp', pattern = "protein.csv", 
                    full.names = TRUE)
files <- lapply(files, read.csv, stringsAsFactors = FALSE)
colnames(files[[1]])[2] <- 'clinvar'; colnames(files[[2]])[2] <- 'cosmic'; colnames(files[[3]])[2] <- 'gnomad_common'; colnames(files[[4]])[2] <- 'gnomad_rare'
files <- Reduce(function(f1, f2) merge(f1, f2, by = "protein"), files)
head(files)
rownames(files) <- files$protein
files <- files[, 2:5]
cdf <- files

hart_essential <- read.table('~/gene_sets/Hart_CRISPR_uniprot.tab', 
                             stringsAsFactors = FALSE,
                             header = TRUE, sep = "\t", comment.char = '', quote = '')
hart_essential <- hart_essential$Entry

# count of the number of genes int the Hart Essential gene set
sum(rownames(cdf) %in% hart_essential)
hart_essential <- cdf[which(rownames(cdf) %in% hart_essential), ]
essential_genes <- readLines('essential_genes/essential_genes_uniprot')
essential_genes <- union(essential_genes, rownames(hart_essential))

#________________________________________
# TCGA all sample
tcga <- list.files(path = "~/TCGA.firehose_maf", 
                   pattern = glob2rx("*_maf_allmuttype_mapped_withSig_new.txt"),
                   full.names = T)
tcga <- tcga[ which(!grepl("TCGA_", tcga)) ]
tcga <- lapply(tcga, function(file){
  maf <- read.table(file, header = T, quote = "", sep = "\t", stringsAsFactors = F)
  # print(summary(as.factor(maf$Variant_Classification)))
  maf$Chromosome <- sapply(maf$Chromosome, function(x){
    out <- gsub("chr", "", x)
    if (!(out %in% c("X", "Y"))) return(as.numeric(out)) else return(out)
  })
  maf$cohort <- unlist(strsplit(basename(file), split ="_"))[1]
  maf
  #split(maf, maf$Tumor_Sample_Barcode, drop = TRUE)
})
tcga <- do.call("rbind", tcga)
tcga <- tcga[ which(tcga$SwissProt_acc_Id %in% essential_genes), ]
tcga <- list(tcga)#tcga <- split(tcga, tcga$Tumor_Sample_Barcode, drop = TRUE)
tcga_all <- lapply(tcga, get_dndscv_input, filter = FALSE)
tcga_surf <- lapply(tcga, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "surface")
tcga_core <- lapply(tcga, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "core")
tcga_all <- lapply(tcga_all, get_dndscv_output_global)
tcga_surf <- lapply(tcga_surf, get_dndscv_output_global)
tcga_core <- lapply(tcga_core, get_dndscv_output_global)

#________________________________________
# hipsci all sample
hipsci <- "hipsci_unique_ProteinAlteringMutations_noHLA_zoomvar.maf"
hipsci <- read.table(hipsci, header = T, sep = "\t", stringsAsFactors = F)
hipsci$cohort <- 'iPSCs'
hipsci <- hipsci[ which(hipsci$SwissProt_acc_Id %in% essential_genes), ]
hipsci <- list(hipsci)#hipsci <- split(hipsci, hipsci$Tumor_Sample_Barcode, drop = TRUE)
hipsci_all <- lapply(hipsci, get_dndscv_input, filter = FALSE)
hipsci_surf <- lapply(hipsci, get_dndscv_input, filter = TRUE, 
                      filterCol = "struct_cat", filter_value = "surface")
hipsci_core <- lapply(hipsci, get_dndscv_input, filter = TRUE, 
                      filterCol = "struct_cat", filter_value = "core")
hipsci_all <- lapply(hipsci_all, get_dndscv_output_global)
hipsci_surf <- lapply(hipsci_surf, get_dndscv_output_global)
hipsci_core <- lapply(hipsci_core, get_dndscv_output_global)

#________________________________________
# ICGC all sample
icgc <- "ICGC_20190603_All_Metastatic_simple_somatic_mutation_exonic_oncotator_noHLA_zoomvar.maf"
icgc <- read.table(icgc, header = T, sep = "\t", stringsAsFactors = F, quote = '')
icgc$cohort <- sapply(icgc$Center, function(x) unlist(strsplit(x, split = "-"))[1])
icgc <- icgc[ which(icgc$SwissProt_acc_Id %in% essential_genes), ]
icgc <- list(icgc)#icgc <- split(icgc, icgc$Tumor_Sample_Barcode, drop = TRUE)
icgc_all <- lapply(icgc, get_dndscv_input, filter = FALSE)
icgc_surf <- lapply(icgc, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "surface")
icgc_core <- lapply(icgc, get_dndscv_input, filter = TRUE, 
                    filterCol = "struct_cat", filter_value = "core")
icgc_all <- lapply(icgc_all, get_dndscv_output_global)
icgc_surf <- lapply(icgc_surf, get_dndscv_output_global)
icgc_core <- lapply(icgc_core, get_dndscv_output_global)

#________________________________________
tcga_all <- data.frame(cohort = "TCGA", genes = "essential genes",
                       dNdS_all = tcga_all[[1]]$mle[1], 
                       cilow_all = tcga_all[[1]]$cilow[1], 
                       cihigh_all = tcga_all[[1]]$cihigh[1],
                       dNdS_surface = tcga_surf[[1]]$mle[1], 
                       cilow_surface = tcga_surf[[1]]$cilow[1], 
                       cihigh_surface = tcga_surf[[1]]$cihigh[1],
                       dNdS_core = tcga_core[[1]]$mle[1], 
                       cilow_core = tcga_core[[1]]$cilow[1], 
                       cihigh_core = tcga_core[[1]]$cihigh[1],
                       stringsAsFactors = FALSE)
saveRDS(tcga_all,file='dNdScv_TCGAallSamples_essential.rds')
hipsci_all <- data.frame(cohort = "HipSci", genes = "essential genes",
                         dNdS_all = hipsci_all[[1]]$mle[1], 
                         cilow_all = hipsci_all[[1]]$cilow[1], 
                         cihigh_all = hipsci_all[[1]]$cihigh[1],
                         dNdS_surface = hipsci_surf[[1]]$mle[1], 
                         cilow_surface = hipsci_surf[[1]]$cilow[1], 
                         cihigh_surface = hipsci_surf[[1]]$cihigh[1],
                         dNdS_core = hipsci_core[[1]]$mle[1], 
                         cilow_core = hipsci_core[[1]]$cilow[1], 
                         cihigh_core = hipsci_core[[1]]$cihigh[1],
                         stringsAsFactors = FALSE)
saveRDS(hipsci_all,file='dNdScv_HipSciallSamples_essential.rds')
icgc_all <- data.frame(cohort = "ICGC Metastatic", genes = "essential genes",
                       dNdS_all = icgc_all[[1]]$mle[1], 
                       cilow_all = icgc_all[[1]]$cilow[1], 
                       cihigh_all = icgc_all[[1]]$cihigh[1],
                       dNdS_surface = icgc_surf[[1]]$mle[1], 
                       cilow_surface = icgc_surf[[1]]$cilow[1], 
                       cihigh_surface = icgc_surf[[1]]$cihigh[1],
                       dNdS_core = icgc_core[[1]]$mle[1], 
                       cilow_core = icgc_core[[1]]$cilow[1], 
                       cihigh_core = icgc_core[[1]]$cihigh[1],
                       stringsAsFactors = FALSE)
saveRDS(icgc_all,file='dNdScv_ICGCallSamples_essential.rds')
```

## Plot

Plot from dNdScv results the central dN/dS estimates with 95% confidence intervals.
Separately for dN/dS calculated over:

* all genes
* CGC drivers only
* essential genes only

```{r fig.width=6, fig.height=5}
#________________________________________
# Analysis
dNdS_all <- list.files(pattern = "dNdScv_.*allSamples.*.rds")
dNdS_all <- lapply(dNdS_all, readRDS)
dNdS_all <- do.call("rbind", dNdS_all)
dNdS_all <- list(dNdS_all[, c("cohort", "genes", "dNdS_all", "cilow_all",
                              "cihigh_all")],
                 dNdS_all[, c("cohort", "genes", "dNdS_surface", "cilow_surface",
                              "cihigh_surface")],
                 dNdS_all[, c("cohort", "genes", "dNdS_core", "cilow_core",
                              "cihigh_core")])
dNdS_all[[1]]$region <- "overall"
dNdS_all[[2]]$region <- "surface"
dNdS_all[[3]]$region <- "core"
colnames(dNdS_all[[1]]) <- c("cohort", "geneset", "dNdS", "cilow", "cihigh", "region")
colnames(dNdS_all[[2]]) <- c("cohort", "geneset", "dNdS", "cilow", "cihigh", "region")
colnames(dNdS_all[[3]]) <- c("cohort", "geneset", "dNdS", "cilow", "cihigh", "region")
dNdS_all <- do.call("rbind", dNdS_all)
dNdS_all$cohort <- factor(dNdS_all$cohort,
                          levels = c("HipSci", "TCGA", "ICGC Metastatic"),
                          labels = c("HipSci iPSCs", "TCGA", "ICGC Metastatic"))
dNdS_all$geneset <- factor(dNdS_all$geneset,
                          levels = c("all", "CGC", "essential genes"),
                          labels = c("all genes", "CGC drivers", "essential genes"))
dNdS_all$region <- factor(dNdS_all$region,
                          levels = c("overall", "surface", "core"))

ggplot(dNdS_all[which(dNdS_all$region != "overall"), ], 
       aes(y = region, x = dNdS)) +
  geom_point() + geom_errorbar(aes(xmin = cilow, xmax = cihigh), width = 0) +
  geom_vline(xintercept = 1, linetype = "dashed") + xlab("dN/dS") + ylab("") +
  cowplot::theme_cowplot() + facet_grid(cohort ~ geneset)

```
